Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-11-24 main.tex
:pencil: Update energy detection rules

			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period. To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$. Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
			\begin{equation}
				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
				\label{eq:received_signal}
			\end{equation}
			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$. Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathcal{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
			\begin{equation}
				h_{\mathrm{E}}^H(\boldsymbol{c}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
				\label{eq:equivalent_channel}
			\end{equation}

@@

			For the ease of notation, we label the backscatter symbol vector by a decimal number that uniquely maps to the modulation index set. As an example, when tag $k$ is at state $m_k$, the modulation index set is $\{m_1,\ldots,m_K\}$, and the backscatter symbol vector can be defined as $\boldsymbol{c}_l \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T$, where $l \in \{1,\ldots,M^K\}$ in decimal equals $m_1 - 1 \ldots m_{K-1} - 1 \ m_K$ in base-$M$.

@@

			% Since the status of all tags remain unchanged over $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary symbol $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution. When the backscatter symbol vector is $\boldsymbol{c}_l$,
			Since the status of all tags remain unchanged over $N$ primary symbols, the received signal is only subject to the variation of the primary source and AWGN. When the backscatter symbol vector is $\boldsymbol{c}_l$, the received signal at block $n$ follows CSCG distribution as
			\begin{equation}
				y_l[n] \sim \mathcal{CN}\biggl(0,\sigma_l^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2\biggr).
			\end{equation}

@@

				\Lambda_{i, j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),

@@

				\Lambda_{i, j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\lessgtr}} 1 \iff z \underset{H_j}{\overset{H_i}{\lessgtr}} T_{i, j},

@@

				T_{i, j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},

@@

			where $p_{i, j}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as

@@

				p_{i, j} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,

@@

			We then investigate the achievable rate of the backscatter link. Denote the tag input probability mass function as $\boldsymbol{r} = [r_1,\ldots,r_M]^T \in \mathbb{R}_+^{M \times 1}$ where $r_m$ is the probability to transmit symbol $c_m$ [strictly positive?]. For a given input distribution $\boldsymbol{r}$ and forward transition matrix $\boldsymbol{P}$, the achievable backscatter rate can be written as
			\begin{equation}
				R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
				\label{eq:secondary_rate}
			\end{equation}
			where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix
			\begin{equation}
				\boldsymbol{Q} \triangleq
				\begin{bmatrix}
					q_{1, 1} & \ldots & q_{1, M} \\
					\vdots & \ddots & \vdots \\
					q_{M, 1} & \ldots & q_{M, M}
				\end{bmatrix},
			\end{equation}
			and $q_{j, i}$ denotes the transition probability from channel output state $j$ to input state $i$.
		\end{subsection}
	\end{section}

@@

			We then investigate the achievable rate of the backscatter link. Denote the tag input probability mass function as $\boldsymbol{r} = [r_1,\ldots,r_M]^T \in \mathbb{R}_+^{M \times 1}$ where $r_m$ is the probability to transmit symbol $c_m$ [strictly positive?]. For a given input distribution $\boldsymbol{r}$ and forward transition matrix $\boldsymbol{P}$, the achievable backscatter rate can be written as
			\begin{equation}
				R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
				\label{eq:secondary_rate}
			\end{equation}
			where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix
			\begin{equation}
				\boldsymbol{Q} \triangleq
				\begin{bmatrix}
					q_{1, 1} & \ldots & q_{1, M} \\
					\vdots & \ddots & \vdots \\
					q_{M, 1} & \ldots & q_{M, M}
				\end{bmatrix},
			\end{equation}
			and $q_{j, i}$ denotes the transition probability from channel output state $j$ to input state $i$.
		\end{subsection}

@@

		\begin{subsection}{Achievable rate region}
			To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the tag input probability mass function, under $M$-PSK modulation, to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{r} \ge 0}}{\rho R_s + (1 - \rho) R_c}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1,}{\label{co:sum_probability}}
			\end{maxi!}
			where $\rho \in [0, 1]$ is the weight factor. By substituting \eqref{eq:secondary_rate} and \eqref{eq:primary_rate} into \eqref{ob:weighted_sum_rate}, the problem expands to
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{r} \ge 0, \boldsymbol{Q} \ge 0}}{\rho \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber}{}{}
				\breakObjective{+ (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}}{r_i}}{\label{ob:weighted_sum_rate_expanded}}
				\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1.}{}
			\end{maxi!}
			Similar to the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972}, we optimize $\boldsymbol{r}$ and $\boldsymbol{Q}$ alternatively to obtain the local optimal tag input distribution and the corresponding weighted sum-rate.
			\begin{theorem}
				For any valid tag input probability mass function $\boldsymbol{r}$ [$\boldsymbol{r} > \boldsymbol{0}$?], the optimal backward transition probability from channel output state $j$ to input state $i$ follows Bayes' Theorem as
				\begin{equation}
					q_{j, i}^{\star} = \frac{r_i p_{i, j}}{\sum_{i'} r_{i'} p_{i', j}}.
					\label{eq:backward_transition}
				\end{equation}
				\label{th:backward_transition}
			\end{theorem}
			\begin{proof}
				Please refer to Appendix~\ref{ap:backward_transition}.
			\end{proof}
			\begin{theorem}
				For any valid backward transition probability $\boldsymbol{Q}$ [$\boldsymbol{Q} \ge 0$?], the optimal tag input probability mass function is given by
				\begin{equation}
					r_i = \frac{\bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i, j}}}{\sum_{i' \in \mathcal{M}} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_{i'} \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i'}^{p_{i', j}}}.
					\label{eq:input_distribution}
				\end{equation}
				\label{th:input_distribution}
			\end{theorem}
			\begin{proof}
				Please refer to Appendix~\ref{ap:input_distribution}.
			\end{proof}
			\begin{proposition}
				For any feasible initial point [constellation subset], the Algorithm is guaranteed to converge to the global optimal of problem \eqref{op:weighted_sum_rate} and achieve the maximum weighted-sum rate.
			\end{proposition}
			\begin{proof}
				The proof is similar to that in \cite[Chapter~9.3]{Yeung2008} and omitted here.
			\end{proof}
		\end{subsection}
	\end{section}

@@

	\begin{appendix}
		\begin{subsection}{Proof of Theorem~\ref{th:backward_transition}}
			Denote the objective function \eqref{ob:weighted_sum_rate_expanded} as $R(\boldsymbol{r}, \boldsymbol{Q})$. Let $w_j \triangleq \sum_{i'} r_{i'} p_{i', j}$ and rearrange \eqref{eq:backward_transition} as
			\begin{equation}
				w_j q_{j, i}^{\star} = r_i p_{i, j}.
			\end{equation}
			Therefore,
			\begin{align}
				R(\boldsymbol{r}, \boldsymbol{Q}^{\star}) - R(\boldsymbol{r}, \boldsymbol{Q})
				& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
				& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} w_j q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
				& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \sum_{i \in \mathcal{M}} q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
				& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \infdiv{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
				& \ge 0,
			\end{align}
			with equality iff $\boldsymbol{Q} = \boldsymbol{Q}^{\star}$.
			\label{ap:backward_transition}
		\end{subsection}
		\begin{subsection}{Proof of Theorem~\ref{th:input_distribution}}
			We employ the method of Lagrange multipliers, temporally ignore the constraint $\boldsymbol{r} \ge 0$, and assume all logarithms are of base $e$. Define the Lagrangian function as
			\begin{align}
				J
				& = \rho \sum_{i \in \mathcal{M}} r_i \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber \\
				& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i, j} \log \frac{q_{j, i}}{r_i} + \lambda \left( 1 - \sum_{i \in \mathcal{M}} r_i \right),
			\end{align}
			where $\lambda$ is the Lagrange multiplier associated with the sum-probability constraint. Differentiating $J$ with respect to $r_i$ gives
			\begin{align}
				\pdv{J}{r_i}
				& = \rho \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \\
				& \quad + (1 - \rho) \left( \sum_{j \in \mathcal{M}} p_{i, j} \log q_{j, i} - \log r_i - 1 \right),
			\end{align}
			and setting $\pdv*{J}{r_i} = 0$ suggests
			\begin{equation}
				r_i = e^{ -(\frac{\lambda}{1 - \rho} + 1)} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i, j}}.
			\end{equation}
			By considering $\sum_{i \in \mathcal{M}} r_i = 1$, we can eliminate $\lambda$ and obtain the optimal tag input distribution as \eqref{eq:input_distribution}.
			\label{ap:input_distribution}
		\end{subsection}
	\end{appendix}

>>>>

			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period. To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$. Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
			\begin{equation}
				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
				\label{eq:received_signal}
			\end{equation}
			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$. Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathcal{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
			\begin{equation}
				h_{\mathrm{E}}^H(\boldsymbol{c}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
				\label{eq:equivalent_channel}
			\end{equation}

@@

			To explicitly specify the content of backscatter symbol vector, we label it by the corresponding modulation index set. For example, when tag $k$ is at state $m_k$, $\forall k \in \mathcal{K}$, the backscatter symbol vector is defined as $\boldsymbol{c}_{\{m_k\}} \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T \in \mathcal{C}^{K \times 1}$. Since any $\boldsymbol{c}_{\{m_k\}}$ remains constant over $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{\{m_k\}}[n] \sim \mathcal{CN}\left(0,\sigma_{\{m_k\}}^2\right)$ with variance
				\sigma_{\{m_k\}}^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2.
				\label{eq:receive_variance}
			Note that $\sigma_{\{m_k\}}^2$ denotes the expectation of the received power per primary block when tag $k$ is at state $m_k$, $\forall k \in \mathcal{K}$, which can be numerically evaluated based on the precoder, tag, channel, and noise knowledge. For the ease of exposition, we sort all possible $\sigma_{\{m_k\}}^2$ in ascending order by a one-to-one mapping $\{m_k\} \mapsto i$, denote the hypothesis that the backscatter symbol vector in status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} For the optimal Maximum-Likelihood (ML) detector, the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
				\label{eq:likelihood_ratio}
			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$ and $f(\boldsymbol{y} \mid \mathcal{H}_j)$ are respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert \boldsymbol{y} \rVert^2$ is the received signal energy over $N$ primary blocks. Obviously, the likelihood ratio only depends on $z$ and the energy detection is thus optimal. The corresponding decision rule is
				\Lambda_{i,j}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j},
				\label{eq:decision_rule}
			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
			On top of this, the decision region of hypothesis $\mathcal{H}_i$ is
			and we manually define $T_{0,1} \triangleq 0$ and $T_{M^K,M^K+1} \triangleq \infty$. Let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
				\label{eq:energy_distribution}
			% where $\Gamma(\cdot)$ is the gamma function. As such, the equivalent discrete memoryless channel can be defined by a transition matrix from $\mathcal{M^K}$ to $\mathcal{M^K}$,\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.} where the probability of observing output state $j$ under input state $i$ is
			where $\Gamma(\cdot)$ is the gamma function. As such, the equivalent discrete memoryless channel can be defined by a transition matrix where the probability of observing output state $j \in \mathcal{M^K}$ under input state $i \in \mathcal{M^K}$ is\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.}
				p(z_j \mid \boldsymbol{c}_i) = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
			In summary, for every candidate backscatter symbol vector, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to the nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the channel transition matrix can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:transition_probability}.

			% the expected power of the received signal per block under all backscatter combinations can be estimated by \eqref{eq:receive_variance}, the energy detection threshold between any backscatter symbol vectors with adjacent

			% can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, and the forward transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}.

			% estimated at the user.

			% To enable energy detection

			% For the ease of notation, we label the backscatter symbol vector by a decimal number that uniquely maps to the modulation index set. As an example, when tag $k$ is at state $m_k$, the modulation index set is $\{m_1,\ldots,m_K\}$, and the backscatter symbol vector can be defined as $\boldsymbol{c}_l \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T$, where $l \in \{1,\ldots,M^K\}$ in decimal equals $m_1 - 1 \ldots m_{K-1} - 1 \ m_K$ in base-$M$.

@@

			% Since the status of all tags remain unchanged over $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary symbol $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution. When the backscatter symbol vector is $\boldsymbol{c}_l$,
			% Since the status of all tags remain unchanged over $N$ primary symbols, the received signal is only subject to the variation of the primary source and AWGN. When the backscatter symbol vector is $\boldsymbol{c}_l$, the received signal at block $n$ follows CSCG distribution as
			% \begin{equation}
			% 	y_l[n] \sim \mathcal{CN}\biggl(0,\sigma_l^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2\biggr).
			% \end{equation}

@@

				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),

@@

				\Lambda_{i,j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\lessgtr}} 1 \iff z \underset{H_j}{\overset{H_i}{\lessgtr}} T_{i,j},

@@

				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},

@@

			where $p_{i,j}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as

@@

				p_{i,j} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z,

@@

			We then investigate the achievable rate of the backscatter link. Denote the tag input probability mass function as $\boldsymbol{r} = [r_1,\ldots,r_M]^T \in \mathbb{R}_+^{M \times 1}$ where $r_m$ is the probability to transmit symbol $c_m$ [strictly positive?]. For a given input distribution $\boldsymbol{r}$ and forward transition matrix $\boldsymbol{P}$, the achievable backscatter rate can be written as
			\begin{equation}
				R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
				\label{eq:secondary_rate}
			\end{equation}
			where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix
			\begin{equation}
				\boldsymbol{Q} \triangleq
				\begin{bmatrix}
					q_{1, 1} & \ldots & q_{1, M} \\
					\vdots & \ddots & \vdots \\
					q_{M, 1} & \ldots & q_{M, M}
				\end{bmatrix},
			\end{equation}
			and $q_{j, i}$ denotes the transition probability from channel output state $j$ to input state $i$.
		\end{subsection}
	\end{section}

@@

			We then investigate the achievable rate of the backscatter link. Denote the tag input probability mass function as $\boldsymbol{r} = [r_1,\ldots,r_M]^T \in \mathbb{R}_+^{M \times 1}$ where $r_m$ is the probability to transmit symbol $c_m$ [strictly positive?]. For a given input distribution $\boldsymbol{r}$ and forward transition matrix $\boldsymbol{P}$, the achievable backscatter rate can be written as
			\begin{equation}
				R_c = \max_{\boldsymbol{Q} \ge 0} \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i} \ [\si{bpcu}],
				\label{eq:secondary_rate}
			\end{equation}
			where $\boldsymbol{Q} \in \mathbb{R}_{+}^{M \times M}$ is the backward transition probability matrix
			\begin{equation}
				\boldsymbol{Q} \triangleq
				\begin{bmatrix}
					q_{1, 1} & \ldots & q_{1, M} \\
					\vdots & \ddots & \vdots \\
					q_{M, 1} & \ldots & q_{M, M}
				\end{bmatrix},
			\end{equation}
			and $q_{j, i}$ denotes the transition probability from channel output state $j$ to input state $i$.
		\end{subsection}

@@

		\begin{subsection}{Achievable rate region}
			To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the tag input probability mass function, under $M$-PSK modulation, to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{r} \ge 0}}{\rho R_s + (1 - \rho) R_c}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1,}{\label{co:sum_probability}}
			\end{maxi!}
			where $\rho \in [0, 1]$ is the weight factor. By substituting \eqref{eq:secondary_rate} and \eqref{eq:primary_rate} into \eqref{ob:weighted_sum_rate}, the problem expands to
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{r} \ge 0, \boldsymbol{Q} \ge 0}}{\rho \sum_{i \in \mathcal{M}} r_i \log_2 \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber}{}{}
				\breakObjective{+ (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}}{r_i}}{\label{ob:weighted_sum_rate_expanded}}
				\addConstraint{\sum_{i \in \mathcal{M}} r_i}{=1.}{}
			\end{maxi!}
			Similar to the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972}, we optimize $\boldsymbol{r}$ and $\boldsymbol{Q}$ alternatively to obtain the local optimal tag input distribution and the corresponding weighted sum-rate.
			\begin{theorem}
				For any valid tag input probability mass function $\boldsymbol{r}$ [$\boldsymbol{r} > \boldsymbol{0}$?], the optimal backward transition probability from channel output state $j$ to input state $i$ follows Bayes' Theorem as
				\begin{equation}
					q_{j, i}^{\star} = \frac{r_i p_{i,j}}{\sum_{i'} r_{i'} p_{i', j}}.
					\label{eq:backward_transition}
				\end{equation}
				\label{th:backward_transition}
			\end{theorem}
			\begin{proof}
				Please refer to Appendix~\ref{ap:backward_transition}.
			\end{proof}
			\begin{theorem}
				For any valid backward transition probability $\boldsymbol{Q}$ [$\boldsymbol{Q} \ge 0$?], the optimal tag input probability mass function is given by
				\begin{equation}
					r_i = \frac{\bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i,j}}}{\sum_{i' \in \mathcal{M}} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_{i'} \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i'}^{p_{i', j}}}.
					\label{eq:input_distribution}
				\end{equation}
				\label{th:input_distribution}
			\end{theorem}
			\begin{proof}
				Please refer to Appendix~\ref{ap:input_distribution}.
			\end{proof}
			\begin{proposition}
				For any feasible initial point [constellation subset], the Algorithm is guaranteed to converge to the global optimal of problem \eqref{op:weighted_sum_rate} and achieve the maximum weighted-sum rate.
			\end{proposition}
			\begin{proof}
				The proof is similar to that in \cite[Chapter~9.3]{Yeung2008} and omitted here.
			\end{proof}
		\end{subsection}
	\end{section}

@@

	\begin{appendix}
		\begin{subsection}{Proof of Theorem~\ref{th:backward_transition}}
			Denote the objective function \eqref{ob:weighted_sum_rate_expanded} as $R(\boldsymbol{r}, \boldsymbol{Q})$. Let $w_j \triangleq \sum_{i'} r_{i'} p_{i', j}$ and rearrange \eqref{eq:backward_transition} as
			\begin{equation}
				w_j q_{j, i}^{\star} = r_i p_{i,j}.
			\end{equation}
			Therefore,
			\begin{align}
				R(\boldsymbol{r}, \boldsymbol{Q}^{\star}) - R(\boldsymbol{r}, \boldsymbol{Q})
				& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
				& = (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} w_j q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
				& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \sum_{i \in \mathcal{M}} q_{j, i}^{\star} \log_2 \frac{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
				& = (1 - \rho) \sum_{j \in \mathcal{M}} w_j \infdiv{q_{j, i}^{\star}}{q_{j, i}} \nonumber \\
				& \ge 0,
			\end{align}
			with equality iff $\boldsymbol{Q} = \boldsymbol{Q}^{\star}$.
			\label{ap:backward_transition}
		\end{subsection}
		\begin{subsection}{Proof of Theorem~\ref{th:input_distribution}}
			We employ the method of Lagrange multipliers, temporally ignore the constraint $\boldsymbol{r} \ge 0$, and assume all logarithms are of base $e$. Define the Lagrangian function as
			\begin{align}
				J
				& = \rho \sum_{i \in \mathcal{M}} r_i \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \nonumber \\
				& \quad + (1 - \rho) \sum_{i \in \mathcal{M}} \sum_{j \in \mathcal{M}} r_i p_{i,j} \log \frac{q_{j, i}}{r_i} + \lambda \left( 1 - \sum_{i \in \mathcal{M}} r_i \right),
			\end{align}
			where $\lambda$ is the Lagrange multiplier associated with the sum-probability constraint. Differentiating $J$ with respect to $r_i$ gives
			\begin{align}
				\pdv{J}{r_i}
				& = \rho \log \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr) \\
				& \quad + (1 - \rho) \left( \sum_{j \in \mathcal{M}} p_{i,j} \log q_{j, i} - \log r_i - 1 \right),
			\end{align}
			and setting $\pdv*{J}{r_i} = 0$ suggests
			\begin{equation}
				r_i = e^{ -(\frac{\lambda}{1 - \rho} + 1)} \bigl( 1 + \gamma \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_i \rvert^2 \bigr)^{\rho / (1 - \rho)} \prod_{j \in \mathcal{M}} q_{j, i}^{p_{i,j}}.
			\end{equation}
			By considering $\sum_{i \in \mathcal{M}} r_i = 1$, we can eliminate $\lambda$ and obtain the optimal tag input distribution as \eqref{eq:input_distribution}.
			\label{ap:input_distribution}
		\end{subsection}
	\end{appendix}
